### 2021-03-16 papers/SYRCoSE/intro.tex
SYRCoSE: finished with new intro

\eupp{Continue from here...}

>>>>

In the programming language and formal semantics research community 
it become the de-facto standard to complement the theoretical 
studies with their mechanization in the \emph{proof assistants}
like Coq, Agda, Isabelle, Arend, and others,
as this process increases the reliability and reproducibility 
of the scientific results.
Yet, as far as we know, there is a little work on 
mechanization of event structures theory.

Our work is aimed to close this gap. 
Our goal is to develop a Coq library containing 
a comprehensive set of common definitions, lemmas, 
and tactics that would allow the researchers 
to utilize the theory of event structures 
for the needs of their domain.

In this work in progress report we sketch 
the common design princples behind our library
and give a concrete example of its usage  
by developing a formal mechanized semantics of simple 
register machine with shared memory.
